### 2010-10-12 papers/BMD2010/PhysicalParametersPaper/paper.tex
bicycle subfigure done

%\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage{subfiles}

@@

\section{Bicycle Descriptions}
\subsection{Yellow Bicycle}
The yellow is a bicycle used in the lab to demonstrate that a bicycle is stable
at certain speeds. It is an aluminum road frame of unknown make with the
majority of components removed. The wheels, drop handlebar, seat, seat post and
bottom bracket are the only parts on the bike. The fork has been reversed to
''increase`` the stability of the bicycle. The bicycle was measured with both
the fork in normal position and the fork reversed.
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/yellow.jpg}
    \end{center}
    \caption{Side view of the yellow bicycle with the fork in the reversed
    posistion.}
    \label{fig:YellowBike}
\end{figure}
\subsection{Batavus Browser}
The Batavus Browser is lower priced Dutch city bike. We measured the physical
proprieties of the stock Browser model and also the same bike with the
instrumentation used in our experiments.
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/browser.jpg}
    \end{center}
    \caption{Side view of the Batavus Browser as from the factory.}
    \label{fig:browser}
\end{figure}
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/browserIns.jpg}
    \end{center}
    \caption{The Batavus Browser with instrumentation as used
    in~\cite{Kooijman2009}}
    \label{fig:browserIns}
\end{figure}

\subsection{2007 Bianchi Pista}
The Pista is a modern steel track bicycle. Specifications, taken from the Bianchi
website~\cite{Bianchi2009}, are as follows:
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/pista.jpg}
    \end{center}
    \caption{The Bianchi Pista hanging from a spring scale.}
    \label{fig:pista}
\end{figure}
\subsection{Gary Fisher Mountain Bike}
The Gary Fisher Ziggurat is a modern front suspended mountain bike.
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/fisher.jpg}
    \end{center}
    \caption{The Gary Fisher mountain bike hanging from a spring scale.}
    \label{fig:fisher}
\end{figure}
\subsection{Batavus Crescendo Deluxe}
The Batavus Crescendo Deluxe is a contemporary of all-round cycling in cool
black and white. A great bike for a good end to touring. And that works fine
with 8 gears, suspension fork and suspension seatpost.
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/crescendo.jpg}
    \end{center}
    \caption{A side view of the Batavus Crescendo Deluxe.}
    \label{fig:crescendo}
\end{figure}
\subsection{Batavus Stratos Deluxe}
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/stratos.jpg}
    \end{center}
    \caption{A side view of the Batavus Stratos Deluxe}
    \label{fig:stratos}
\end{figure}
\section{Accuracy}
Error propagation theory was utilized to calculate what the accuracy the
benchmark ideal parameters are based on the measurements taken. If $x$ is a
random variable and is defined as $x=f(u,v,\ldots)$ then the sample variance of
$x$ is defined as
\begin{equation}
    s_x^2 = \frac{1}{N-1}\sum^N_{i=1}
    \left[(u_i - \bar{u})^2\left(\frac{\partial x}{\partial u}\right)^2 +
    (v_i - \bar{v})^2\left(\frac{\partial x}{\partial v}\right)^2 +
    2(u_i - \bar{u})(v_i - \bar{v})\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
    + \ldots\right]
    \label{eqn:sampleVariance}
\end{equation}
Using the definitions for variance and covariance
Equation~\ref{eqn:sampleVariance} can be simplified to
\begin{equation}
    s_x^2 = s_u^2\left(\frac{\partial x}{\partial u}\right)^2 +
            s_v^2\left(\frac{\partial x}{\partial v}\right)^2 +
            2s_{uv}\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
            + \ldots
    \label{eqn:variance}
\end{equation}
If $u$ and $v$ are uncorrelated then $s_{uv}=0$. We assume that the all the
random variables hereafter are uncorrelated. Equation~\ref{eqn:variance} can be
used to calculated the variance of all types of functions. The most basic are
functions such as addtion
\begin{eqnarray}
    \label{eqn:addition}
    x &=&  au + bv\\
    s_x &=& a^2s_u^2 + b^2s_v^2
\end{eqnarray}

>>>>

%\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage{subfiles}
\usepackage{subfig}

@@

\section{Bicycle Descriptions}
\begin{description}
    \item[Batavus Browser]{The Batavus Browser is lower priced Dutch city bike.
        We measured the physical proprieties of the stock Browser model and
        also the same bike with the instrumentation used in our experiments.}
    \item[Batavus Crescendo Deluxe]{The Batavus Crescendo Deluxe is a
        contemporary of all-round cycling in cool black and white. A great bike
        for a good end to touring. And that works fine with 8 gears, suspension
        fork and suspension seatpost.}
    \item[Gary Fisher Mountain Bike]{The Gary Fisher Ziggurat is a modern front
        suspended mountain bike.}
    \item[2007 Bianchi Pista]{The Pista is a modern steel track bicycle.}
    \item[Batavus Stratos Deluxe]{Is a Dutch sport bicycle.}
    \item[Yellow Bicycle]{The yellow is a bicycle used in the lab to
        demonstrate that a bicycle is stable at certain speeds. It is an
        aluminum road frame of unknown make with the majority of components
        removed. The wheels, drop handlebar, seat, seat post and bottom bracket
        are the only parts on the bike. The fork has been reversed to
        ''increase``~\cite{Kooijman2006} the stability of the bicycle. The
        bicycle was measured with both the fork in normal position and the fork
        reversed.}
\end{description}
\begin{figure}[htbp]
    \centering
    \subfloat[Batavus Browser]{
        \label{fig:browser}\includegraphics[width=1.75in]{../../../images/browserIns_sub.jpg}}
    \subfloat[Batavus Crescendo Deluxe]{
        \label{fig:crescendo}\includegraphics[width=1.75in]{../../../images/crescendo_sub.jpg}}
    \subfloat[Gary Fisher]{
        \label{fig:fisher}\includegraphics[width=1.75in]{../../../images/fisher_sub.jpg}}
        \\
    \subfloat[Bianchi Pista]{
        \label{fig:pista}\includegraphics[width=1.75in]{../../../images/pista_sub.jpg}}
    \subfloat[Batavus Stratos Deluxe]{
        \label{fig:stratos}\includegraphics[width=1.75in]{../../../images/stratos_sub.jpg}}
    \subfloat[Yellow Bicycle]{
        \label{fig:yellow}\includegraphics[width=1.75in]{../../../images/yellow_sub.jpg}}
    \caption{The six bicycles measured in the experiments. The Batavus
    Browser~\subref{fig:browser} is shown with the instrumentation and the
    Yellow Bicycle~\subref{fig:yellow} is shown with its fork reversed.}
    \label{fig:bicycles}
\end{figure}
\section{Accuracy}
Error propagation theory was utilized to calculate what the accuracy the
benchmark ideal parameters are based on the measurements taken. If $x$ is a
random variable and is defined as $x=f(u,v,\ldots)$ then the sample variance of
$x$ is defined as
\begin{equation}
    s_x^2 = \frac{1}{N-1}\sum^N_{i=1}
    \left[(u_i - \bar{u})^2\left(\frac{\partial x}{\partial u}\right)^2 +
    (v_i - \bar{v})^2\left(\frac{\partial x}{\partial v}\right)^2 +
    2(u_i - \bar{u})(v_i - \bar{v})\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
    + \ldots\right]
    \label{eqn:sampleVariance}
\end{equation}
Using the definitions for variance and covariance
Equation~\ref{eqn:sampleVariance} can be simplified to
\begin{equation}
    s_x^2 = s_u^2\left(\frac{\partial x}{\partial u}\right)^2 +
            s_v^2\left(\frac{\partial x}{\partial v}\right)^2 +
            2s_{uv}\left(\frac{\partial x}{\partial u}\right)\left(\frac{\partial x}{\partial v}\right)
            + \ldots
    \label{eqn:variance}
\end{equation}
If $u$ and $v$ are uncorrelated then $s_{uv}=0$. We assume that the all the
random variables hereafter are uncorrelated. Equation~\ref{eqn:variance} can be
used to calculated the variance of all types of functions. The most basic are
functions such as addtion
\begin{eqnarray}
    \label{eqn:addition}
    x &=&  au + bv\\
    s_x &=& a^2s_u^2 + b^2s_v^2
\end{eqnarray}
